Near Optimal Behavior via Approximate State Abstraction

### 2016-02-05 paper/theory_results.tex
Cleaned up some optimal Q notation
formatting misc

% Theorem 1
\begin{thm}
There exist at least four classes of approximate state-aggregation functions, $\epQ$, $\epM$, $\epB$ and $\epMu$, for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\frac{1}{\epsilon}$:
\begin{equation}
\forall_{s \in \mathcal{S}_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) \leq poly \left (\frac{1}{\epsilon} \right).
\end{equation}
\end{thm}
\enote{Axe the absolute values here and elsewhere}

\enote{Unify the use of $\forall$ and ``:"s}

\enote{Add for 0-1 normalized reward}

\enote{Add note relating this all to Lihong for eps=0 and cut down the Lihong section}

@@

Note that as $t \rightarrow \infty$, $\sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} \rightarrow \frac{2\epsilon}{(1-\gamma)^2}$ by the sum of geometric series and $\pi_{A,t}(s) \rightarrow \pi_{GA}$.
Thus, we conclude Lemma~\ref{lma:Q*}.
%\begin{equation*}
%\forall_{s_G \in \mathcal{S}_g} V_G(s_G) \leq  V_G^{\pi_{GA}}(s_G) + \frac{2\epsilon}{(1-\gamma)^2}
%\end{equation*}
%\begin{equation*}
%\forall_{s_G \in \mathcal{S}_g} \left | V_G(s_G) - V_G^{\pi_{GA}}(s_G) \right | \leq  \frac{2\epsilon}{(1-\gamma)^2}
%\end{equation*}

@@

\bdefn{$\epB$}
We let $\epB$ define a family of abstractions that, for fixed $\epsilon$, satisfies:
\begin{multline}
\epB(s_1) = \epB(s_2) \rightarrow \\
\forall_{a} \left|\frac{e^{Q_G^*(s_1,a)}}{\sum_b e^{Q_G^*(s_1,b)}} - \frac{e^{Q_G^*(s_2,a)}}{\sum_b e^{Q_G^*(s_2,b)}}\right| \leq \epsilon.
\label{eq:phi_bolt}
\end{multline}
\edefn
\dnote{Possible explanation of what Boltzmann does in language, here}

We also assume that the difference in normalizing terms is bounded by some non-negative constant, $k\in \mathbb{R}$, of $\epsilon$:
\begin{equation}
\left| \sum_b e^{Q_G^*(s_1,b)} - \sum_b e^{Q_G^*(s_2,b)} \right| \leq k\times\epsilon.
\label{eq:bolt_denom}
\end{equation}
\begin{lma} When $S_A$ is created using a function of the $\epB$ type, for some non-negative constant $k \in \mathbb{R}$:
\begin{equation}
\forall_{s \in \mcS_G} V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) \leq \frac{2\epsilon\left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k\right)}{(1-\gamma)^2}.
\end{equation}
\label{lma:bolt_lemma}
\end{lma}
We prove Lemma~\ref{lma:bolt_lemma} using the approximation for $e^x$:
\begin{equation}
 e^x = 1 + x + \delta  \approx 1 + x
\label{eq:e_to_x_approx}
\end{equation}
where $\delta$ is the error associated with the approximation.

@@

We consider approximate abstractions derived from a multinomial distribution over $Q^*$ for similar reasons to our motivation in considering the Boltzmann distribution. \dnote{Relationship between multi and bolts, why need this one, argument: it's simpler! simpler is good}
\bdefn{$\epMu$}
We let $\epMu$ define a type of abstraction that, for fixed $\epsilon$, satisfies
\begin{multline}
\epMu(s_1) = \epMu(s_2) \rightarrow \\
\forall_{a} \left|\frac{Q_G^*(s_1,a)}{\sum_b Q_G^*(s_1,b)} - \frac{Q_G^*(s_1,a)}{\sum_b Q_G^*(s_1,b)}\right| \leq \epsilon.
\end{multline}
\edefn
\dnote{Some explanation of what this one does}

>>>>

% Theorem 1
\begin{thm}
There exist at least four classes of approximate state-aggregation functions, $\epQ$, $\epM$, $\epB$ and $\epMu$, for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\frac{1}{\epsilon}$:
\begin{equation}
\forall_{s \in \mathcal{S}_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{GA}}(s) \leq poly \left (\frac{1}{\epsilon} \right).
\end{equation}
\end{thm}

@@

Note that as $t \rightarrow \infty$, $\sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} \rightarrow \frac{2\epsilon}{(1-\gamma)^2}$ by the sum of infinite geometric series and $\pi_{A,t}(s) \rightarrow \pi_{GA}$.
Thus, we conclude Lemma~\ref{lma:Q*}.
%\begin{equation*}
%\forall_{s_G \in \mathcal{S}_g} V_G(s_G) \leq  V_G^{\pi_{GA}}(s_G) + \frac{2\epsilon}{(1-\gamma)^2}
%\end{equation*}
%\begin{equation*}
%\forall_{s_G \in \mathcal{S}_g} \left | V_G(s_G) - V_G^{\pi_{GA}}(s_G) \right | \leq  \frac{2\epsilon}{(1-\gamma)^2}
%\end{equation*}

@@

\bdefn{$\epB$}
We let $\epB$ define a family of abstractions that, for fixed $\epsilon$, satisfies:
\begin{multline}
\epB(s_1) = \epB(s_2) \rightarrow \\
\forall_{a} \left|\frac{e^{Q_G(s_1,a)}}{\sum_b e^{Q_G(s_1,b)}} - \frac{e^{Q_G(s_2,a)}}{\sum_b e^{Q_G(s_2,b)}}\right| \leq \epsilon.
\label{eq:phi_bolt}
\end{multline}
\edefn
\dnote{Possible explanation of what Boltzmann does in language, here}

We also assume that the difference in normalizing terms is bounded by some non-negative constant, $k\in \mathbb{R}$, of $\epsilon$:
\begin{equation}
\left| \sum_b e^{Q_G(s_1,b)} - \sum_b e^{Q_G(s_2,b)} \right| \leq k\times\epsilon.
\label{eq:bolt_denom}
\end{equation}
\begin{lma} When $S_A$ is created using a function of the $\epB$ type, for some non-negative constant $k \in \mathbb{R}$:
\begin{equation}
\forall_{s \in \mcS_G} V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) \leq \frac{2\epsilon\left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k\right)}{(1-\gamma)^2}.
\end{equation}
\label{lma:bolt_lemma}
\end{lma}
We prove Lemma~\ref{lma:bolt_lemma} using the approximation for $e^x$:
\begin{equation}
 e^x = 1 + x + \delta  \approx 1 + x
\label{eq:e_to_x_approx}
\end{equation}
where $\delta$ is the error associated with the approximation.

@@

We consider approximate abstractions derived from a multinomial distribution over $Q^*$ for similar reasons to our motivation in considering the Boltzmann distribution. \dnote{Relationship between multi and bolts, why need this one, argument: it's simpler! simpler is good}
\bdefn{$\epMu$}
We let $\epMu$ define a type of abstraction that, for fixed $\epsilon$, satisfies
\begin{multline}
\epMu(s_1) = \epMu(s_2) \rightarrow \\
\forall_{a} \left|\frac{Q_G(s_1,a)}{\sum_b Q_G(s_1,b)} - \frac{Q_G(s_1,a)}{\sum_b Q_G(s_1,b)}\right| \leq \epsilon.
\end{multline}
\edefn
\dnote{Some explanation of what this one does}
